---
title: "Ling620 Final Project: Analysis"
output: rmdformats::lockdown
pkgdown:
  as_is: true  
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width=11,
                      fig.height=5,
                      fig.asp = 0.6,
                      out.width = "100%",
                      fig.align = "center")
```

```{r message=FALSE}
library(tidyverse)
library(broom)
library(gridExtra)
library(here)
library(janitor)
library(lmerTest)
library(ggplot2)
library(Hmisc)
library(arm)
library(wesanderson)
library(broom.mixed)
library(kableExtra)

theme_set(theme_light())
```

```{r message=FALSE}
aqchoice <- read_csv(here("data", "AQChoiceData.csv"))

ascchoice <- read_csv(here("data", "ASCChoiceData.csv"))

attributes <- read_csv(here("data", "Attributes.csv"))
```

There are two parallel studies, i.e. two independent datasets coded AQ and ASC. This section will cover how the datasets were preprocessed, some exploratory data analysis (EDA), and the actual modelling of the data.

## Preprocessing  

- All participants were presented with six "catch trials". 
- Catch trials are testing whether the participant is paying attention and following the instructions.
- Participants who failed in responding correctly to 3 or more catch trials were excluded because they probably were not paying attention or following instructions.  
```{r}
aqchoice %>% 
  group_by(Pcp) %>% 
  summarise(Catchfail = mean(Catchfail)) %>% 
  arrange(-Catchfail) %>% 
  filter(Catchfail >= 3) %>% 
  pull(Pcp) -> failed_pcps_aq

ascchoice %>% 
  group_by(Pcp) %>% 
  summarise(Catchfail = mean(Catchfail)) %>% 
  arrange(-Catchfail) %>% 
  filter(Catchfail >= 3) %>% 
  pull(Pcp) -> failed_pcps_asc
```  

- Some response times are extremely long (up to two hours), and these values are clearly outliers even among individual participant responses.
- A cutoff point was decided for response time corresponding to two standard deviations in each dataset. 

```{r}
cutoffpoint <- sd(aqchoice$Dur*2, na.rm = TRUE)/1000 # ~2 minutes cutoff

cutoffpoint <- sd(ascchoice$Dur*2, na.rm = TRUE)/1000 # ~5 minutes cutoff
```

- As a next step we filtered the remaining data as follows:  
a) kept trials with response times smaller to the corresponding cutoff points,  
b) catch trials were excluded,  
c) trials where participants chose the decoy were excluded (we were not interested in modeling these odd responses),  
d) we excluded one participant who prefered not to say their gender due to the difficulty of establishing and interpreting the contrast corresponding to this isolated piece of data.  

- Then we centered and rescaled (dividing by two standard deviations) the continuous variables, and applied a centered contrast-coding scheme (Helmert contrasts) for categorical variables.  

- Finally, we created the following variables:  
a) `match` -- whether the chosen product corresponds to the target; and
b) `sensory` -- whether the attributes listed for the product in a trial include a sensory attribute.  

The resulting datasets (`aqchoice_tidy`and `ascchoice_tidy`) constitute the main datasets used in the rest of the analysis.

```{r}
aqchoice_tidy <- aqchoice %>%
  clean_names() %>%
  filter(dur/1000 < cutoffpoint,
         catch == 0,
         choice != "D",
         gender != "PNTS",
         !pcp %in% failed_pcps_aq,
         version == 1) %>%  
  mutate(
    # version = factor(version),
    pcp = factor(pcp),
    dur_log = log(dur),
    dur_std = rescale(dur),
    set = factor(set),
    choice = factor(choice),
    pos1 = factor(pos1),
    pos2 = factor(pos2),
    pos3 = factor(pos3),
    target = factor(target),
    a_qgroup = factor(a_qgroup),
    icar_std = rescale(icar),
    aq_score_std = rescale(aq_score),
    trial_std = arm::rescale(trial),
    age_std = rescale(age),
    gender = factor(gender),
    nationality = factor(nationality),
    aut = factor(aut),
    match = factor(ifelse(choice == target, 1, 0), levels = c(1,0), labels = c("yes", "no")),
    sensory = factor(case_when(
      product == "apartment" ~ 1,
      product == "cell phone" ~ 0,
      product == "couch" ~ 1,
      product == "headphones" ~ 1,
      product == "highlighter" ~ 1,
      product == "job" ~ 0,
      product == "notebook" ~ 0,
      product == "orange juice" ~ 0,
      product == "paper towels" ~ 0,
      product == "printer" ~ 0,
      product == "screen" ~ 1,
      product == "second-hand book" ~ 0,
      product == "shares" ~ 0,
      product == "USB drive" ~ 0,
      product == "vacuum cleaner" ~ 1,
      TRUE ~ 1
    )),
    sen_dom = case_when(
      product == "apartment" ~ "B",
      product == "couch" ~ "B",
      product == "headphones" ~ "B",
      product == "highlighter" ~ "B",
      product == "screen" ~ "A",
      product == "vacuum cleaner" ~ "A",
      product == "walking shoes" ~ "A",
      TRUE ~ NA_character_
    )
  )


contrasts(aqchoice_tidy$a_qgroup) <- contr.helmert(2)/2
contrasts(aqchoice_tidy$gender) <- contr.helmert(2)/2
contrasts(aqchoice_tidy$aut) <- contr.treatment(3)
contrasts(aqchoice_tidy$target) <- contr.helmert(2)/2
contrasts(aqchoice_tidy$choice) <- contr.helmert(2)/2
contrasts(aqchoice_tidy$match) <- contr.helmert(2)/2
contrasts(aqchoice_tidy$sensory) <- contr.helmert(2)/2

# Note: the following piece of code can be erased once all instances of "aq_sensory" below are replaced by "aqchoice_tidy". 
aq_sensory <- aqchoice_tidy
```


```{r}
ascchoice_tidy <- ascchoice %>% 
  clean_names() %>% 
  filter(dur/1000 < cutoffpoint,
         catch == 0,
         choice != "D",
         gender != "PNTS",
         !pcp %in% failed_pcps_asc) %>% 
  mutate(
    pcp = factor(pcp),
    set = factor(set),
    choice = factor(choice),
    pos1 = factor(pos1),
    pos2 = factor(pos2),
    pos3 = factor(pos3),
    target = factor(target),
    dur_log = log(dur),
    dur_std = arm::rescale(dur),
    asc = factor(asc, levels = c(0,1), labels = c("no", "yes")),
    icar_std = arm::rescale(icar),
    aq_score_std = arm::rescale(aq_score),
    age_std = arm::rescale(age),
    gender = factor(gender),
    residence = factor(residence),
    set = factor(set),
    trial_std = arm::rescale(trial),
    comorbid = factor(comorbid, levels = c(0,1), labels = c("no", "yes")),
    match = factor(ifelse(choice == target, 1, 0), levels = c(1,0), labels = c("yes", "no")),
    sensory = factor(case_when(
      product == "apartment" ~ 1,
      product == "cell phone" ~ 0,
      product == "couch" ~ 1,
      product == "headphones" ~ 1,
      product == "highlighter" ~ 1,
      product == "job" ~ 0,
      product == "notebook" ~ 0,
      product == "orange juice" ~ 0,
      product == "paper towels" ~ 0,
      product == "printer" ~ 0,
      product == "screen" ~ 1,
      product == "second-hand book" ~ 0,
      product == "shares" ~ 0,
      product == "USB drive" ~ 0,
      product == "vacuum cleaner" ~ 1,
      TRUE ~ 1
    )),
    sen_dom = case_when(
      product == "apartment" ~ "B",
      product == "couch" ~ "B",
      product == "headphones" ~ "B",
      product == "highlighter" ~ "B",
      product == "screen" ~ "A",
      product == "vacuum cleaner" ~ "A",
      product == "walking shoes" ~ "A",
      TRUE ~ NA_character_
    )
         )  %>% 
  droplevels()


contrasts(ascchoice_tidy$match) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$choice) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$target) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$asc) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$gender) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$sensory) <- contr.helmert(2)/2
contrasts(ascchoice_tidy$match) <- contr.helmert(2)/2



# Note: the following piece of code can be erased once all instances of "asc_sensory" below are replaced by "ascchoice_tidy". 
asc_sensory <- ascchoice_tidy 
```  

A variation of these main datasets was created. This variation has one observation per participant and product, and has a variable (`consistent`) that checks whether the second time that the participant encountered a given product, they chose the same instance. That is, presumably, whether they changed their choice when the decoy targeted another instance of the product.  

```{r}
aq_consistent <- aqchoice_tidy %>% 
  # filter(catch == 0) %>% 
  dplyr::select(pcp, dur_std, dur_log, age_std, gender, a_qgroup, trial, trial_std, choice, target, product, adom, bdom, sensory, sen_dom) %>% 
  group_by(pcp, product) %>% 
  filter(n() == 2) %>% 
  mutate(timing = ifelse(trial == max(trial), 2, 1)) %>% 
  arrange(timing) %>% 
  ungroup() %>% 
  group_by(pcp, product) %>%
  mutate(consistent = duplicated(choice),
         # sensory = factor(sensory),
         product = factor(product),
         timing = factor(timing),
         consistent = factor(ifelse(consistent == FALSE, 0, 1), levels = c(0,1), labels = c("no","yes")))


# Some of the following lines may be redundant, but they harm not.
contrasts(aq_consistent$gender) <- contr.helmert(2)/2
contrasts(aq_consistent$a_qgroup) <- contr.helmert(2)/2
contrasts(aq_consistent$choice) <- contr.helmert(2)/2
contrasts(aq_consistent$target) <- contr.helmert(2)/2
contrasts(aq_consistent$sensory) <- contr.helmert(2)/2
contrasts(aq_consistent$timing) <- contr.helmert(2)/2
contrasts(aq_consistent$consistent) <- contr.helmert(2)/2
```


```{r}
asc_consistent <- ascchoice_tidy %>% 
  # filter(catch == 0) %>% 
  dplyr::select(pcp, dur_std, dur_log, age_std, gender, asc, trial, trial_std, choice, target, product, adom, bdom, sensory, sen_dom) %>% 
  group_by(pcp, product) %>% 
  filter(n() == 2) %>% 
  mutate(timing = ifelse(trial == max(trial), 2, 1)) %>% 
  arrange(timing) %>% 
  ungroup() %>% 
  group_by(pcp, product) %>%
  mutate(consistent = duplicated(choice),
         # sensory = factor(sensory),
         product = factor(product),
         timing = factor(timing),
         consistent = factor(ifelse(consistent == FALSE, 0, 1), levels = c(0,1), labels = c("no","yes")))


# Some of the following lines may be redundant, but they harm not.
contrasts(asc_consistent$gender) <- contr.helmert(2)/2
contrasts(asc_consistent$choice) <- contr.helmert(2)/2
contrasts(asc_consistent$sensory) <- contr.helmert(2)/2
contrasts(asc_consistent$target) <- contr.helmert(2)/2
contrasts(asc_consistent$timing) <- contr.helmert(2)/2
contrasts(asc_consistent$asc) <- contr.helmert(2)/2
contrasts(asc_consistent$consistent) <- contr.helmert(2)/2
```

## Exploratory data analysis  

The following plot depicts the response time distribution for the participants in each of the two studies. Response times in the AQ study were less disperse.
```{r}
ggplot(data = aqchoice) +
  geom_histogram(aes(x = Dur/1000), fill = wes_palette("Darjeeling2", 2)[2], alpha = .5) +
  geom_histogram(aes(x = Dur/1000), data = ascchoice, fill = wes_palette("Darjeeling2", 3)[3], alpha = .5) +
  xlim(c(0, 1e5/1000)) +
  labs(x = "Response time in seconds", y = "Count",
       caption = "blue = AQ study; yellow = ASC study") 
```

The following (actually useless -- could be a table) plots show how observations are distributed across groups and target matching, for each study.   
```{r}
tb <- table(aqchoice_tidy$match, aqchoice_tidy$a_qgroup)

tb2 <- tibble(
  a_qgroup = factor(c("H", "H", "L", "L")),
  match = factor(c("no", "yes", "no", "yes")),
  label = c(tb[2], tb[1], tb[4], tb[3])
)

p1 <- aqchoice_tidy %>%  # switch L and H around
  ggplot(aes(x = a_qgroup, y = match)) +
  geom_jitter(color = "steelblue", alpha = 0.4) +
  geom_label(aes(label = label), data = tb2) +
  labs(x = "AQ group", y = "Choice - Target match", 
       caption = paste("Fisher's exact test p-value = ", round(fisher.test(tb)$p.value, digits = 2)))

tb <- table(ascchoice_tidy$match, ascchoice_tidy$asc) 
#note for later: would be interesting to see the same thing but with actual reported autistics and otherwise

tb2 <- tibble(
  asc = factor(c("yes", "yes", "no", "no")),
  match = factor(c("no", "yes", "no", "yes")),
  label = c(tb[4], tb[3], tb[2], tb[1])
)

p2 <- ascchoice_tidy %>% 
  ggplot(aes(x = asc, y = match)) +
  geom_jitter(color = wes_palette("Darjeeling1", 1), alpha = 0.4) +
  geom_label(aes(label = label), data = tb2) +
  labs(x = "Autism spectrum condition", y = "Choice - Target match", 
       caption = paste("Fisher's exact test p-value = ", round(fisher.test(tb)$p.value, digits = 6))) 

grid.arrange(p1, p2, nrow = 1)
```  
```{r}
tb <- table(aq_consistent$consistent, aq_consistent$a_qgroup)

tb2 <- tibble(
  a_qgroup = factor(c("H", "H", "L", "L")),
  consistent = factor(c("no", "yes", "no", "yes")),
  label = c(tb[2], tb[1], tb[4], tb[3])
)

p1 <- aq_consistent %>%  # switch L and H around
  ggplot(aes(x = a_qgroup, y = consistent)) +
  geom_jitter(color = "steelblue", alpha = 0.4) +
  geom_label(aes(label = label), data = tb2) +
  labs(x = "AQ group", y = "Consistent choice", 
       caption = paste("Fisher's exact test p-value = ", round(fisher.test(tb)$p.value, digits = 2)))

tb <- table(asc_consistent$consistent, asc_consistent$asc) 
#note for later: would be interesting to see the same thing but with actual reported autistics and otherwise

tb2 <- tibble(
  asc = factor(c("yes", "yes", "no", "no")),
  consistent = factor(c("no", "yes", "no", "yes")),
  label = c(tb[4], tb[3], tb[2], tb[1])
)

p2 <- asc_consistent %>% 
  ggplot(aes(x = asc, y = consistent)) +
  geom_jitter(color = wes_palette("Darjeeling1", 1), alpha = 0.4) +
  geom_label(aes(label = label), data = tb2) +
  labs(x = "Autism spectrum condition", y = "Consistent choice", 
       caption = paste("Fisher's exact test p-value = ", round(fisher.test(tb)$p.value, digits = 6))) 

grid.arrange(p1, p2, nrow = 1)
```

These distributions, with their corresponding Fisher's exact test p-value suggest that in both studies there seems to be a tendency for a) scoring high vs low on the AQ test, and b) having an autism spectrum condition vs being neurotypical, respectively, to influece whether the participants chose the target product (i.e. the one cued by the decoy).  But more so in the ASC study.   

The following plots depict how, for each study, the response times display a downward trend the later the trial. This will motivate the inclusion of trial number as a control predictor in later modelling. This notion is further confirmed by an exploratory simple linear model. Notably, there does not seem to be a significant interaction between asc condition and trial number, but there seems to be such an interaction between aq group and trial number.  
```{r}
p1 <- ascchoice_tidy %>% 
  ggplot(aes(x = trial, y = dur/1000)) +
  stat_summary(geom = "line", aes(group = asc, color = asc)) +
  labs(x = "Trial", y = "Response time (seconds)", color = "ASC", title = "ASC study") +
  scale_color_manual(values = c(wes_palette("Darjeeling2", 3)[2:3]))
summary(mod <- lm(dur_log ~ trial_std * asc, data = ascchoice_tidy))


p2 <- aqchoice_tidy %>% 
  mutate(a_qgroup = ifelse(a_qgroup == "H", "High", "Low")) %>% 
  ggplot(aes(x = trial, y = dur/1000)) +
  stat_summary(geom = "line", aes(group = a_qgroup, color = a_qgroup)) +
  labs(x = "Trial", y = "Response time (seconds)", color = "AQ Group", title = "AQ study") +
  scale_color_manual(values = c(wes_palette("Darjeeling2", 5)[c(3,5)]))
summary(mod <- lm(dur_log ~ trial_std * a_qgroup, data = aqchoice_tidy))

grid.arrange(p1, p2, nrow = 2)
```

Extra exploratory data analysis -- not discussed, but may be useful?
```{r fig.height=20}
p1 <- aqchoice_tidy %>% 
  filter(version == 1) %>% 
  ggplot(aes(x = dur_log, fill = a_qgroup)) +
  geom_density(alpha = .5) +
  labs(x = "Response time (log)", y = "Density", fill = "AQ group", title = "Reponse time distribution by product") +
  scale_fill_manual(values = wes_palette("Darjeeling1", 4)[2:3]) +
  facet_wrap(~ product)

p2 <- ascchoice_tidy %>% 
  ggplot(aes(x = dur_log, fill = asc)) +
  geom_density(alpha = .7) +
  labs(x = "Response time (log)", y = "Density", fill = "ASC", title = "Reponse time distribution by product") +
  scale_fill_manual(values = wes_palette("Darjeeling1", 2)) +
  facet_wrap(~ product) 

grid.arrange(p1, p2, nrow = 2)
```

## Statistical modelling

### Fixed effects modeling
A basic fixed effects model includes: response time (in log scale) as a function of: 
- autistic spectrum condition / AQ score group
- whether the presented stimulus includes sensory attributes,
- the interaction of these (we expect the ASC status to modulate the effect of sensory attribute presence), 
- whether the participant chose the target product (the one cued by the decoy; we expect the decision to choose the target option to be quicker than other decisions),
- age (control; maybe younger people will respond quicker),
- gender (control)  
```{r}
mod_fixed_aq_2 <- lm(dur_log ~ a_qgroup * sensory + match + trial_std + age_std + gender, data = aq_sensory)
summary(mod_fixed_aq_2)

mod_fixed_asc_2 <- lm(dur_log ~ asc * sensory + match + trial_std + age_std + gender, data = asc_sensory)
summary(mod_fixed_asc_2) # no interaction effect, consistent with chi2 test
```    

AQ study:
- trial and age are significant
- AQ score group, presence of sensory attribute, and matched choice display a tendency but do not reach significance
  
ASC study:
- ASC condition, sensory attributes, matched choice, trial number, and age display a significant effect on response time; 

### Random effects modeling
The main random effects model has the same fixed effects, but is added the following random effects:
- by-participant random intercepts,
- by-participant random slopes of sensory attribute presence,
- by-product random intercepts,
- by-product random slopes of ASC/AQ condition  

(Additionally, to deal with convergence issues, the random categorical terms are numerically recoded.)


```{r results='hide'}
# This is the model for the AQ study.
mod_random_aq_4 <- lmer(dur_log ~ a_qgroup * sensory + trial_std + match + age_std + gender +
                           (1 + sensory || pcp) +
                           (1 + a_qgroup || product), 
                         data = aq_sensory,
                         REML = TRUE,
                         control = lmerControl(optimizer ='bobyqa'))

mm <- model.matrix(mod_random_aq_4) %>% data.frame()
aq_sensory <- add_column(aq_sensory, a_qgroup1 = mm$a_qgroup1)
aq_sensory <- add_column(aq_sensory, sensory1 = mm$sensory1)

#  |||||
#  |||||
#  |||||
# VVVVVVV 
#  VVVVV
#    V

mod_random_aq_4 <- lmer(dur_log ~ a_qgroup * sensory + trial_std + match + age_std + gender +
                           (1 + sensory1 || pcp) +
                           (1 + a_qgroup1 || product), 
                         data = aq_sensory,
                         REML = TRUE,
                         control = lmerControl(
                           optimizer ='optimx', optCtrl=list(method='nlminb'))
                           )

summary(mod_random_aq_4) # nothing interesting but probably true
```
```{r}
# Regression table
whole <- tidy(mod_random_aq_4) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```    
This model's output displays the same significant terms as the fixed effects model; however, it seems to be controlling the effect of the other predictors, after accounting for random effects, so that they do not display any tendency to be significant anymore. It shows that the by-participant groupings display substantial intercept variability (s.d. around 0.3), but little slope variability. The by-product variability is small both in intercept and slopes.   

This is the model for the ASC study.
```{r results='hide'}
mod_random_asc_4 <- lmer(dur_log ~ asc * sensory + trial_std +  match + age_std + gender +
                           (1 + sensory || pcp) +
                           (1 + asc || product), 
                         data = asc_sensory,
                         REML = TRUE,
                         control = lmerControl(optimizer ='bobyqa'))

mm <- model.matrix(mod_random_asc_4) %>% data.frame()
asc_sensory <- add_column(asc_sensory, sensory1 = mm$sensory1)
asc_sensory <- add_column(asc_sensory, asc1 = mm$asc1)

#  |||||
#  |||||
#  |||||
# VVVVVVV 
#  VVVVV
#    V


mod_random_asc_4 <- lmer(dur_log ~ asc * sensory + trial_std +  match + age_std + gender +
                           (1 + sensory1 || pcp) +
                           (1 + asc1 || product), 
                         data = asc_sensory,
                         REML = TRUE,
                         control = lmerControl(optimizer ='bobyqa'))

summary(mod_random_asc_4) 
# note that the model is singular, but that's okay, our model is not actually too complex, and it should not affect its interpretation. Moreover, we are not *especially* interested in the random terms that display 0 variance. Finally, that 0 variance could be that it is simply very very little. 
```      

```{r}
# Regression table
whole <- tidy(mod_random_asc_4) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```    
This linear mixed effects model displays very similar results to the corresponding fixed effects model, just with greater p-values. In a sense, it may be that accounting for random effects is controlling the effect and significance of these predictors. It also shows that both product and participant groupings display substantial intercept variability (s.d. around 0.5), but little slope variability.   

A further model was fit using the alternative dataset (the one with consistency). This model additionally takes the predictors of whether the participant made a consistent decision the second time a product was presented, as well as the interaction of ASC/AQ condition with consistency (as one important prediction is that asc/aq traits should impact judgement criteria when choosing an instance of a product).

For the AQ study:
```{r results='hide'}

const_random_aq_1 <- lmer(dur_log ~ a_qgroup * consistent + sensory + trial_std + age_std + gender + 
                             (1 + sensory || pcp) +
                             (1 + a_qgroup + consistent || product)
                           , data = aq_consistent
                           , REML = TRUE
                           , control = lmerControl(optimizer ='bobyqa'))

mm <- model.matrix(const_random_aq_1) %>% data.frame()
aq_consistent <- add_column(aq_consistent, a_qgroup1 = mm$a_qgroup1)
aq_consistent <- add_column(aq_consistent, consistent1 = mm$consistent1)
aq_consistent <- add_column(aq_consistent, sensory1 = mm$sensory1)

const_random_aq_1 <- lmer(dur_log ~ a_qgroup + consistent + sensory + trial_std + age_std + gender + 
                            a_qgroup:consistent + a_qgroup:sensory +
                             (1 + sensory1 || pcp) +
                             (1 + a_qgroup1 + consistent1 || product)
                           , data = aq_consistent
                           , REML = TRUE
                           , control = lmerControl(optimizer ='bobyqa'))

summary(const_random_aq_1) 
```
```{r}
# Regression table
whole <- tidy(const_random_aq_1) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```    
  
That the model displays significance for the effect of consistence suggests that consistent decision making is faster! Furthermore, the interaction of AQgroup and consistency displays a tendency for significance, even if it does not reach it. This is consistend with one of the relevant hypotheses. Moreover, the effect of sensory attributes holds.

For the ASC study:
```{r results='hide'}
const_random_asc_1 <- lmer(dur_log ~ asc * consistent + sensory + trial_std + age_std + gender + 
                             (1 + sensory || pcp) +
                             (1 + asc + consistent || product)
                           , data = asc_consistent
                           , REML = TRUE
                           , control = lmerControl(optimizer ='bobyqa'))

mm <- model.matrix(const_random_asc_1) %>% data.frame()
asc_consistent <- add_column(asc_consistent, asc1 = mm$asc1)
asc_consistent <- add_column(asc_consistent, consistent1 = mm$consistent1)
asc_consistent <- add_column(asc_consistent, sensory1 = mm$sensory1)

const_random_asc_1 <- lmer(dur_log ~ asc + consistent + sensory + trial_std + age_std + gender +
                             asc:consistent + asc:sensory +
                             (1 + sensory1 || pcp) +
                             (1 + asc1 + consistent1  || product)
                           , data = asc_consistent
                           , REML = TRUE
                           , control = lmerControl(optimizer ='bobyqa'))


summary(const_random_asc_1) 
```  
```{r}
# Regression table
whole <- tidy(const_random_asc_1) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```   
The conclusions from the other study are more robust with this sample and model.  
  
Finally we perform a logistic regression looking to replicate the results of the original paper but, moreover, we seek to determine whether there is an effect of sensory attributes to be seen (however, it is not the case).


```{r results='hide'}
#AQ study:
const_subset <- aq_consistent %>% filter(timing == 2) 

const_fixed_aq_1 <- glm(consistent ~ sensory * a_qgroup + dur_std + trial_std + gender
                           , data = const_subset, family = "binomial")

summary(const_fixed_aq_1) 
# Super interesting: these are the same results that the authors found, + we found an effect of sensory attributes. Let's see if this holds in mixed models.

const_random_aq_1 <- glmer(consistent ~ sensory * a_qgroup + dur_std + trial_std + gender +
                            (1 + sensory1 || pcp) +
                            (1 + a_qgroup1 || product) 
                           , data = const_subset, family = "binomial"
                           , control = glmerControl(optimizer ='bobyqa'))
                           
summary(const_random_aq_1) 
```  
```{r}
# Regression table
whole <- tidy(const_random_aq_1) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```  

For the ASC study:
```{r results='hide'}
const_subset <- asc_consistent %>% filter(timing == 2) 
  
const_fixed_asc_1 <- glm(consistent ~ sensory * asc + dur_std + trial_std + gender
                           , data = const_subset, family = "binomial")

summary(const_fixed_asc_1) 

const_random_asc_2 <- glmer(consistent ~ sensory * asc + dur_std + trial_std + gender +
                            (1 + sensory1 || pcp) +
                            (1 + asc1 || product) 
                           , data = const_subset, family = "binomial"
                           , control = glmerControl(optimizer ='bobyqa'))
                           

summary(const_random_asc_2) # holds
```  
```{r}
# Regression table
whole <- tidy(const_random_asc_2) 

fixed <- whole %>% filter(effect == "fixed") %>% dplyr::select(term:p.value)

random <- whole %>% filter(effect != "fixed") %>% 
  dplyr::select(group:estimate) %>% 
  separate(term, c("type", "term")) %>% 
  rename(value = estimate)

kable(fixed, digits = 3, align = NULL, padding = 0) %>%
  kable_paper("striped", full_width = TRUE)

kable(random, digits = 3, align = NULL, padding = 2) %>%
  kable_styling("striped", full_width = TRUE)
```   
Furthermore, there is a significant effect of gender, which suggests that males are more consistent than females in the ASC study.

[Click here pls](https://twitter.com/PHDcomics/status/1465319646622412803/photo/1)


```{r}
aqchoice_tidy %>% 
  group_by(pcp) %>% 
  summarise(mean_dur_min = mean(dur/1000),
            age = mean(age),
            a_qgroup = mean(as.numeric(a_qgroup))) %>% 
  ungroup() %>%
  ggplot(aes(x = age, y = mean_dur_min)) +
  geom_smooth(method = "lm")
  stat_summary(geom = "line", aes(group = a_qgroup))
  # geom_line(aes(group = 1))
```

Partial effect plots
```{r}
library(ggeffects)
p1 <- ggpredict(mod_random_asc_4, terms = c("trial_std", "asc", "match")) %>% plot() +
  labs(x = "Trial (standardized)", y = "Response time (log)", title = "Predicted values of response time (log)",
       subtitle = "Panels = did participants choose the targeted option?", color = "ASC") +
  scale_color_manual(values = wes_palette("GrandBudapest2", 2))

p2 <- ggpredict(mod_random_aq_4, terms = c("trial_std", "a_qgroup", "match")) %>% plot() +
  labs(x = "Trial (standardized)", y = "Response time (log)", title = "Predicted values of response time (log)",
       subtitle = "Panels = did participants choose the targeted option?", color = "ASC") +
  scale_color_manual(values = wes_palette("Darjeeling1", 2))

ggdraw() +
  draw_plot(plot_grid(p1, p2, nrow = 2))
```

```{r}
ascchoice_tidy %>% 
  ggplot(aes())
```



